On g~0~

### 2017-03-27 manuscript.Rmd
fixed references again

- we need g0 to get responses at low light correct, and probably at high T
- g0 is poorly estimated as the intercept, with the usual regression technique
- can we estimate g0 independently? Some assume that g0 = gdark but that's rubbish. It is also much larger than cuticular conductance, but seems roughly consistent with gmin (minimum conductance from leaf dry-down curves).
- there is inter-specific variation in gmin that is related to growth form 
- gmin is a plastic trait as it responds to growth at elevated temperature, and growth in dry soil
- models should consider night-time conductance and daily minimum conductance as distinctly separate processes.

@@

\
(3)
$$ A_n = \frac{a \cdot (C-i - \Gamma^{*})}{C_i + b} - R_d$$

@@

The difficulty of this can be seen from the fact that a) many studies set g0 to something rather than fitting it (e.g. @leuning1995 uses 0.01 for all); presumably because unreliable estimates were obtained, b) negative fitted values are common [@leuning1995; @heroult2013; @miner2016].

@@

**Figure 3**. Correlation between estimated g~0~ and the R^2^ of the regression. In the left panel, we fitted the linearized form of the Medlyn et al. (2011) model to each of the datasets in the Lin et al. (2015) database. Vertical lines are 95% confidence intervals. In the right panel, a very similar association between g~0~ and R^2^ is presented by the review of Miner et al. (2017), using the Ball-Berry model.

>>>>

- we need g0 to get responses at low light correct, and probably at high T
- g0 is poorly estimated as the intercept, with the usual regression technique
- can we estimate g0 independently? Some assume that g0 = gdark (also @miner2017 !) but that's rubbish. It is also much larger than cuticular conductance, but seems roughly consistent with gmin (minimum conductance from leaf dry-down curves).
- there is inter-specific variation in gmin that is related to growth form 
- gmin is a plastic trait as it responds to growth at elevated temperature, and growth in dry soil
- models should consider night-time conductance and daily minimum conductance as distinctly separate processes.

@@

\
(3)
$$ A_n = \frac{a \cdot (C_i - \Gamma^{*})}{C_i + b} - R_d$$

@@

The difficulty of this can be seen from the fact that a) many studies set g0 to something rather than fitting it (e.g. @leuning1995 uses 0.01 for all); presumably because unreliable estimates were obtained, b) negative fitted values are common [@leuning1995; @heroult2013; @miner2017].

@@

**Figure 3**. Correlation between estimated g~0~ and the R^2^ of the regression. In the left panel, we fitted the linearized form of the Medlyn et al. (2011) model to each of the datasets in the Lin et al. (2015) database. Vertical lines are 95% confidence intervals. In the right panel, a very similar association between g~0~ and R^2^ is presented by the review of @miner2017, using the Ball-Berry model.
